Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
use vectors for vars in sigma

The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
that is updated incrementally.
Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$.
%
If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to {\sc verify}, which determines whether it does satisfy
the specification on all inputs by checking satisfiability of the following 
verification formula:
%
$\exists x . \lnot \sigma(x, P)$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set, and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
Given that the full set of inputs $\mathcal{D}$ 
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship between the char. poly. $S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
%
We consider the following form for $S(z)$:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}

>>>>

The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
consists of two phases, {\sc Synthesise} and {\sc Verify}, which
interact via a finite set of test vectors {\sc inputs} that is updated
incrementally.  Given the aforementioned specification $\sigma$, the
{\sc synth} procedure tries to find an existential witness $\vec{P}$
satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}$.
%
If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to {\sc verify}, which determines whether
it does satisfy the specification on all inputs by checking
satisfiability of the following verification formula:
%
$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates.
Otherwise, the witness $\vec{x}$ denote an input on which the
candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
added to the {\sc inputs} set, and the loop iterates again.  It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ being used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship
%% between the char. poly. $S(z)$ and the later quantities $\Delta
%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
%% structure.]}.
%
We consider the following form for $S(z)$:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
